%------------------------------------------------------------------------------
% Preamble
%------------------------------------------------------------------------------
%{{{1
\documentclass[a4paper,12pt]{article}

\usepackage[left=1.0in, right=1.0in, top=1.0in, bottom=1.0in]{geometry}

\usepackage{enumitem}
  \setlist{nolistsep,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

\usepackage{tabto}

\setlength{\parskip}{2\baselineskip}
\setlength{\parindent}{0pt}

\newcommand{\lskip}[1]{\hspace*{1em}\\[#1\baselineskip]}

\newenvironment{Itemize}[0]{
  \vspace{-\parskip}\begin{itemize}\interlinepenalty10000
}{
  \end{itemize}
}
%}}}1


\begin{document}


%------------------------------------------------------------------------------
% Name & address
%------------------------------------------------------------------------------
%{{{1
\begin{center}
{\large\textbf{Jeremy L. Iverson}}\\
Curriculum Vitae\\
%\today
\end{center}
%
\lskip{-3}
%
213 Peter Engel Science Center\hfill XXXX\\
Saint John's University\hfill XXXX\\
Collegeville, MN 56321-3000\hfill\\ % chktex 8
(320) 363-3083\hfill (XXX) XXX-XXXX\\ % chktex 8
jiverson002@csbsju.edu
%}}}1


%------------------------------------------------------------------------------
\textbf{EDUCATION}
%------------------------------------------------------------------------------
%{{{1
\lskip{1}
%
2010--2017  \tabto{7em}UNIVERSITY OF MINNESOTA, Minneapolis, MN\\
            \tabto{7em}Ph.D. in Computer Science, Expected Fall 2017\\
            %\tabto{8em}Dissertation Title: ``Big Data MPI''\\
            \tabto{8em}Dissertation Adviser: George Karypis\\
            \tabto{7em}M.S. in Computer Science, 2013\\
%
\lskip{0}
%
2006--2010  \tabto{7em}SAINT JOHN'S UNIVERSITY, Collegeville, MN\\
            \tabto{7em}B.A. in Computer Science, 2010
%}}}1


%------------------------------------------------------------------------------
\textbf{PUBLICATIONS}
%------------------------------------------------------------------------------
%{{{1
\lskip{1}
%
\textbf{Refereed Journal Articles}
\begin{Itemize}
  \item[2017] ``A virtual memory manager optimized for node-level cooperative
              multi-tasking in memory constrained systems.''. Jeremy Iverson
              and George Karypis. \textit{The International Journal of High
              Performance Computing Applications}, 2017.
  \item[2015] ``Evaluation of Connected-Component Labeling Algorithms for
              Distributed-Memory Systems''. Jeremy Iverson, George Karypis, and
              Chandrika Kamath. \textit{Parallel Computing}, Volume 44, 53--68,
              2015.
\end{Itemize}
%
\lskip{-2}
%
\textbf{Book Chapters}
\begin{Itemize}
  \item[2014] ``Big Data Frequent Pattern Mining''. David Anastasiu, Jeremy
              Iverson, Shaden Smith, and George Karypis. In ``\textit{Frequent
              Pattern Mining}'', Charu C. Aggarwal and Jiawei Han (eds).
              Springer International Publishing, Switzerland, 2014.
\end{Itemize}
%
\lskip{-2}
%
\textbf{Conference Proceedings}
\begin{Itemize}
  \item[2015] ``A Memory Management System Optimized for BDMPI's Memory and
              Execution Model''. Jeremy Iverson and George Karypis. EuroMPI
              2015.
  \item[2012] ``Fast and Effective Lossy Compression Algorithms for Scientific
              Datasets''. Jeremy Iverson, Chandrika Kamath, and George Karypis.
              Euro-Par 2012: 843--856.
  \item[2010] ``Using Metrics to Quantify Similarity in Source Code: An
              Empirical Study Using VOCS''. Jeremy Iverson, James Schnepf, and
              Imad Rahal. SEDE 2010: 269--274.
\end{Itemize}
%
\lskip{-2}
%
\textbf{Technical Reports}
\begin{Itemize}
  \item[2014] ``Storing Dynamic Graphs: Speed vs. Storage Trade-offs''. Jeremy
              Iverson and George Karypis. University of Minnesota Technical
              Report TR14-018, 2014. % chktex 8
  \item[2012] ``Detection of Coherent Structures in Extreme-Scale
              Simulations''. Chandrika Kamath, Jeremy Iverson, and George
              Karypis. Lawrence Livermore National Laboratory Technical Report
              LLNL-CONF-541611, 2012.
\end{Itemize}
%}}}1


%------------------------------------------------------------------------------
\textbf{CONFERENCE PARTICIPATION}
%------------------------------------------------------------------------------
%{{{1
\lskip{1}
%
\textbf{Papers Presented}
\begin{Itemize}
  \item[2015] ``A Memory Management System Optimized for BDMPI's Memory and
              Execution Model''. EuroMPI, September 21--23.

  \item[2012] ``Fast and Effective Lossy Compression Algorithms for Scientific
              Datasets''. Euro-Par, August 27--31.

  \item[2010] ``Using Metrics to Quantify Similarity in Source Code: An
              Empirical Study Using VOCS''. SEDE, June 16--18.
\end{Itemize}
%}}}1


%------------------------------------------------------------------------------
\textbf{TEACHING EXPERIENCE}
%------------------------------------------------------------------------------
%{{{1
\lskip{1}
%
\textbf{Saint John's University, Collegeville, MN}\\
%
Concepts of Computing: Science and Applications, Instructor (F16,S17)\\
%
Introduction to Problem-Solving and Programming, Instructor (F16,S17,F17)\\
%
Principles of Parallel Computing, Instructor (F17)\\
%
\lskip{0}
%
\textbf{University of Minnesota, Minneapolis, MN}\\
%
Introduction to Parallel Computing, Co-instructor (S16)\\
  \hspace*{1em}{\footnotesize Design and deliver weekly lectures, design and
    grade assignments, and hold office hours.}\\
%
Introduction to Parallel Computing, Teaching Assistant (S12)\\
  \hspace*{1em}{\footnotesize Gave two guest lectures, held office hours, and
    graded assignments.}\\
%
Discrete Structures of Computer Science, Teaching Assistant (F10)\\
  \hspace*{1em}{\footnotesize Lead weekly recitations, held office hours, and
    graded assignments.}%\\
%
%\lskip{0}
%
%\textbf{Saint John's University, Collegeville, MN}\\
%
%{\footnotesize Responsibilities for all courses were to monitor weekly labs and
%hold office hours.}\\
%
%Computing: Science and Its Applications, Teaching Assistant (F08,S10)\\
%
%Introduction to Problem-Solving and Programming, Teaching Assistant (S09)\\
%
%Problem Solving, Programming and Data Representation, Teaching Assistant (F09)
%}}}1


%------------------------------------------------------------------------------
%\textbf{RESEARCH EXPERIENCE}
%------------------------------------------------------------------------------
%{{{1
%\lskip{1}
%
%Fall 2010   \tabto{7em}Research Assistant (adviser: George Karypis)\\
%to Present  \tabto{7em}Department of Computer Science\\
%            \tabto{7em}University of Minnesota, Minneapolis, MN\\
%
%\lskip{0}
%
%Summer 2011 \tabto{7em}Research Intern (adviser: Chandrika Kamath)\\
%and 2012    \tabto{7em}Institute for Scientific Computing Research\\
%            \tabto{7em}Lawrence Livermore National Laboratory, Livermore, CA\\
%
%\lskip{0}
%
%Summer 2009 \tabto{7em}Undergraduate Research Assistant (adviser: James Schnepf)\\
%            \tabto{7em}Department of Computer Science\\
%            \tabto{7em}Saint John's University, Collegeville, MN
%}}}1


%------------------------------------------------------------------------------
\textbf{SERVICES TO PROFESSION}
%------------------------------------------------------------------------------
%{{{1
\lskip{0}
%
\begin{Itemize}
  \item[2014] Reviewer for \textit{Transactions on Knowledge Discovery from
              Data}.

  \item[2014] Reviewer for \textit{Transactions on Services Computing}.

  \item[2013] Reviewer for \textit{Transactions on Knowledge and Data
              Engineering}.

  \item[2012] Reviewer for \textit{Journal of Parallel and Distributed
              Computing}.
\end{Itemize}
%}}}1


%------------------------------------------------------------------------------
%\textbf{COURSES PREPARED TO TEACH}
%------------------------------------------------------------------------------
%{{{1
%\lskip{1}
%
%Introduction to Programming, Discrete Mathematics, Algorithms and Data
%Structures, Systems Programming, Computational Complexity, Data Mining,
%Parallel Computing
%}}}1


%------------------------------------------------------------------------------
%\textbf{REFERENCES}
%------------------------------------------------------------------------------
%{{{1
%\lskip{1}
%
%George Karypis, Ph.D., Professor\\
%Department of CSE - UMN Twin Cities\\
%4-192 Kenneth H Keller Hall\\
%Minneapolis, MN 55455\\
%(612) 626-7524\\
%karypis@cs.umn.edu\\
%
%\lskip{0}
%
%Chandrika Kamath, Ph.D.\\
%Center for Applied Scientific Computing - LLNL\\
%Livermore, CA, 94550\\
%(925) 423-3768\\
%kamath2@llnl.gov\\
%
%\lskip{0}
%
%Aziz Mohaisen, Ph.D., Assistant Professor\\
%Department of CSE - SUNY Buffalo\\
%323 Davis Hall\\
%Buffalo, NY, 14260\\
%(716) 645-1592\\
%mohaisen@buffalo.edu
%}}}1


\end{document}
